---
title: "Using Leaflet"
author: "Aman Jindal"
date: "2 September 2020"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, comment='', message=FALSE, warning=FALSE)
```

### 1. Introduction: 
In this document we will make an interactive map in R using the leaflet package. We will plot the location of the following places on an interactive map.

<ol type = 'a'>
    <li> <b> United Nations Headquarters: </b> Latitude  = 40.7489, Longitude = -73.9680 </li>
    <li> <b> Times Square: </b> Latitude  = 40.7580, Longitude = -73.9855 </li>
    <li> <b> Empire State Building: </b> Latitude  = 40.7484, Longitude = -73.9857 </li> 
    <li> <b> Rockfeller Center: </b> Latitude  = 40.7587, Longitude = -73.978 7</li>
</ol>
    
### 2. Making a Leaflet Interactive Plot with Popups:


```{r}
library(leaflet)

df <- data.frame(lat = c(40.7489, 40.7580, 40.7484, 40.7587),
                 lng = c(-73.9680, -73.9855, -73.9857, -73.9787),
                 popup = c('United Nations Headquarters',
                           'Times Square',
                           'Empire State Building',
                           'Rockfeller Center'))

df %>%
    leaflet() %>%
    addTiles() %>%
    addMarkers(popup = df$popup)

```

    
    
